---
title: "candy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
```

```{r}
library(here)
library(tidyverse)
library(janitor)
```

```{r}
candy_2015 <- read_excel(here("Raw_data/boing-boing-candy-2015.xlsx"))
candy_2015
```

```{r}
candy_2016 <- read_excel(here("Raw_data/boing-boing-candy-2016.xlsx"))
```

```{r}
candy_2017 <- read_excel(here("Raw_data/boing-boing-candy-2017.xlsx"))
```

```{r}
candy_2015
```

```{r}
candy_2016
```
```{r}
candy_2017

```

```{r}
glimpse(candy_2016)
```

# adding in a new column to the 2016 data to give it the same number of columns as 2015


```{r}
candy_2016$new <- NULL
```

#Tidying up the column names so they're consistent across all three and easier to work with. 

```{r}
candy_2015 <- clean_names(candy_2015)
candy_2016 <- clean_names(candy_2016)
candy_2017 <- clean_names(candy_2017)
```

```{r}
candy_2015

```

```{r}
candy_2015_long <- candy_2015 %>%
  pivot_longer(cols = c("butterfinger":"york_peppermint_patties"), 
               names_to = "candy_type",
               values_to = "description")

candy_2015_long 
```


```{r}
candy_2015_long <- candy_2015_long[grep("^please", colnames(candy_2015_long), invert = TRUE)]
candy_2015_long
```
#removing extraneous columns

```{r}
candy_2015_long <- select(candy_2015_long, -guess_the_number_of_mints_in_my_hand,  -check_all_that_apply_i_cried_tears_of_sadness_at_the_end_of, 
-that_dress_that_went_viral_early_this_year_when_i_first_saw_it_it_was, 
-fill_in_the_blank_taylor_swift_is_a_force_for, 
-what_is_your_favourite_font, 
-if_you_squint_really_hard_the_words_intelligent_design_would_look_like, 
-fill_in_the_blank_imitation_is_a_form_of,
-sea_salt_flavored_stuff_probably_chocolate_since_this_is_the_it_flavor_of_the_year,
-necco_wafers, -which_day_do_you_prefer_friday_or_sunday)

candy_2015_long
```
```{r}
candy_2015_long <- select(candy_2015_long, -timestamp, -betty_or_veronica)

candy_2015_long
```

```{r}
candy_2015_long
```
#renaming columns so they're more easily manageable
```{r}
candy_2015_long <- rename(candy_2015_long, age = how_old_are_you)
```

```{r}
candy_2015_long <- rename(candy_2015_long, Trick_or_treat = are_you_going_actually_going_trick_or_treating_yourself)
```

```{r}
candy_2015_long

```

#adding in a country column because i'll need that to bind the three years on top of each other later. 

```{r}
candy_2015_long <- mutate(
  candy_2015_long, country = "n/a"
)
```

```{r}
candy_2015_long
```

#adding in a gender column because i'll need that too


```{r}
candy_2015_long <- mutate(
  candy_2015_long, gender = "n/a"
)
```

```{r}
candy_2015_long <- mutate(
  candy_2015_long, county = "n/a"
)
```



#moving to the 2016 data

```{r}
candy_2016
```
#starting with renaming columns this time

```{r}
candy_2016 <- candy_2016 %>% 
  rename(trick_or_treat = are_you_going_actually_going_trick_or_treating_yourself) 
```

```{r}
candy_2016 <- candy_2016 %>% 
  rename(gender = your_gender) 
```

```{r}
candy_2016 <- candy_2016 %>% 
  rename(age = how_old_are_you) 
```

#startign to remove useless column names

```{r}
candy_2016 <-
  select(candy_2016, -timestamp, -york_peppermint_patties_ignore, -which_day_do_you_prefer_friday_or_sunday)

```
#removing all those columns that start with please
```{r}
candy_2016 <- candy_2016[grep("^please", colnames(candy_2016), invert = TRUE)]
candy_2016
```
#renaming column to match 2015
```{r}
candy_2016 <- candy_2016 %>% 
  rename(country = which_country_do_you_live_in)

```


```{r}
candy_2016

```

```{r}
candy_2016 <- candy_2016 %>% 
  rename(county = state)
```


```{r}
candy_2016_longer <- candy_2016 %>%
  pivot_longer(cols = c("x100_grand_bar":"york_peppermint_patties"), 
               names_to = "candy_type",
               values_to = "description")

candy_2016_longer
```


```{r}
candy_2016_longer <- candy_2016_longer %>%
  pivot_longer(cols = c("x100_grand_bar":"boxo_raisins"), 
               names_to = "candy_type",
               values_to = "description")

candy_2016_longer
```

#removing more unwanted columns
```{r}
candy_2016_longer <-
  select(candy_2016_longer, trick_or_treat, gender, age, country, county, candy_type, description)
candy_2016_longer
```

```{r}
colnames(candy_2015_long)
```


#moving onto the 2017 data
#removing the column name suffixes

```{r}
candy_2017 <- candy_2017 %>% 
  rename_all(funs(str_replace(., "q6_", ""))) %>%
  rename_all(funs(str_replace(., "q5_", ""))) %>%
  rename_all(funs(str_replace(., "q4_", ""))) %>%
  rename_all(funs(str_replace(., "q3_", ""))) %>%
  rename_all(funs(str_replace(., "q2_", ""))) %>%
  rename_all(funs(str_replace(., "q1_", ""))) %>%
  rename_all(funs(str_replace(., "q7_", ""))) %>%
  rename_all(funs(str_replace(., "q8_", ""))) %>%
  rename_all(funs(str_replace(., "q9_", ""))) %>%
  rename_all(funs(str_replace(., "q10_", ""))) %>%
  rename_all(funs(str_replace(., "q11_", ""))) %>%
  rename_all(funs(str_replace(., "q12_", ""))) 
  
```

#renaming some columns to match 2015 & 2016
```{r}
candy_2017 <- candy_2017 %>% 
  rename(state = state_province_county_etc) 
 

```
```{r}
candy_2017 <- candy_2017 %>%
  rename(x100_grand_bar = "100_grand_bar")
```

```{r}
candy_2017 <-
  select(candy_2017, -timestamp, -york_peppermint_patties_ignore, -which_day_do_you_prefer_friday_or_sunday)
```


```{r}
candy_2017 <-
  select(candy_2017, -bonkers_the_board_game, -chick_o_sticks_we_don_t_know_what_that_is,  
         -creepy_religious_comics_chick_tracts, -dental_paraphenalia, -generic_brand_acetaminophen, 
         -glow_sticks, -gum_from_baseball_cards, -healthy_fruit, -hugs_actual_physical_hugs,                                        -real_housewives_of_orange_county_season_9_blue_ray, -sandwich_sized_bags_filled_with_boo_berry_crunch, 
         -vials_of_pure_high_fructose_corn_syrup_for_main_lining_into_your_vein, 
         -vicodin, -white_bread, -whole_wheat_anything, -joy_other, -despair_other, -other_comments, -dress, -x114, 
         -day, -media_daily_dish, -media_science, -media_espn, -media_yahoo, -click_coordinates_x_y
           )
```

```{r}
candy_2017 <-
  select(candy_2017, -internal_id)
```

```{r}
candy_2017 <- candy_2017 %>% 
  rename(toblerone = tolberone_something_or_other) %>%
  rename(sweetums = sweetums_a_friend_to_diabetes) %>%
  rename(sourpatch_kids = sourpatch_kids_i_e_abominations_of_nature) 
  
  
```

```{r}
colnames(candy_2017)
```
#all years now have the same columns plus candy, time to pivot longer
```{r}
candy_2017 <- candy_2017 %>% 
  rename(county = state)
```


```{r}
candy_2017_long <- candy_2017 %>%
  pivot_longer(cols = c("x100_grand_bar":"york_peppermint_patties"), 
               names_to = "candy_type",
               values_to = "description")

candy_2017_long 
```

```{r}
candy_2015_long <- clean_names(candy_2015_long)
candy_2016_longer <- clean_names(candy_2016_longer)
candy_2017_long <- clean_names(candy_2017_long)
```

```{r}
colnames(candy_2016_longer)
```

#had to go back and remove more useless columns

```{r}
candy_2016_longer <-
  select(candy_2016_longer, -when_you_see_the_above_image_of_the_4_different_websites_which_one_would_you_most_likely_check_out_please_be_honest, -do_you_eat_apples_the_correct_way_east_to_west_side_to_side_or_do_you_eat_them_like_a_freak_of_nature_south_to_north_bottom_to_top, -what_is_your_favourite_font, -betty_or_veronica, -guess_the_number_of_mints_in_my_hand)
```

```{r}
candy_2016_longer <-
  select(candy_2016_longer, -that_dress_that_went_viral_a_few_years_back_when_i_first_saw_it_it_was)
```

#to match the other years

```{r}
candy_2016_longer <- candy_2016_longer %>% 
  rename(county = state)
```

```{r}
colnames(candy_2017_long)
```

#changing to match other years

```{r}
candy_2017_long <- candy_2017_long %>% 
  rename(trick_or_treat = going_out)
```

#Joing the three years together

```{r}
candy_all <- bind_rows(candy_2015_long, candy_2016_longer, candy_2017_long)
```

```{r}
candy_all
table(candy_all$age)
```


```{r}
tidy_candy <- candy_all %>%
  filter(!is.na(age) > 122)

tidy_candy 
```
```{r}

unique(candy_all$age)
```
#gettign rid of everything that is not NA in the age column. 
```{r}
new_candy <- candy_all %>%
  filter (!is.na(age), nchar(age) > 0)

```

#using 100 as an arbritary cut off point for max age.  poss that i'm losing some genuine entries but unlikely given sample size it will affect outcome to any great degree. 

```{r}
new_candy <- new_candy %>%
  filter(age <= 100) %>%
  filter(age >= 5)
```

#checking for unique entries

```{r}
unique(new_candy$age)
```

```{r}

trick<- select(new_candy, age, trick_or_treat)
        trick

```


```{r}
trick_yes <- filter(trick, trick_or_treat == "Yes")
trick_yes
```
```{r}
mean(trick_yes$age)
```

```{r}
candy_all

```



```{r}
write_csv(candy_all, here("Clean_data/candy_all.csv"))

```


