---
title: "candy_analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
candy_all
```
#What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values

```{r}
unique(candy_all$candy_type)
```

```{r}
ratings <- filter(candy_all, description %in% c("JOY","DESPAIR", "MEH")) 
nrow(ratings)
```

#What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?


```{r}
trick_yes <- filter(trick, trick_or_treat == "Yes")
trick_yes
```

#average age of those who went trick or treating

```{r}
mean(trick_yes$age)
```

#average age of those who did not go trick or treating

```{r}
trick_no <- filter(trick, trick_or_treat == "No")

```


```{r}
mean(trick_no$age)
```
#For each of joy, despair and meh, which candy bar received the most of these ratings?

```{r}
candy_all %>%
  filter(description == "JOY") %>%
  group_by(candy_type) %>%
  print
```


